Fundamental Problems with the Evidence Base of Adolescent Depression Treatments.

### 2024-01-18 apples_and_oranges.qmd
Added in filtering for no wl and no wl or cau regressions. Checked study counts and they all seem correct.

# Use those ids to subset all dataframes in the list
# By searching for IDs we have mistakenly included multiple active arms. E.g. for Atkinson which has dulox and fluox. 
# So we need to further subset the simulated dfs. For the active arms, I am filtering out conditions that do not meet our criterion. 
# This leaves all the control conditions from trials where the active is cbt, fluox or esc. 
# We may have multiple controls per study id for this reason, though this isn't a problem 
# conceptually.

@@

# count the number of studies
cbt_fluox_esc_study <- df_long_for_metan %>%
  filter(new_study_id %in% cbt_fluox_esc_study_ids,
         !(arm_effect_size == "cohens_d_active" & !(type %in% c("Fluoxetine", "Escitalopram", "cbt")))) 
study_count_cbt_fluox_esc_study <- count_studies(cbt_fluox_esc_study)

@@

# C. Estimate Means and CIs without WL ---------------------------------------
# grab the ids for no waitlist
no_wl_ids <-df_appl_v_orange[df_appl_v_orange$control_type != "wl",]$new_study_id

# use them to loop over the simulated list to subset all the dataframes.
list_no_wl <- list()

  list_no_wl[[i]] <- list_df_simulated[[i]][list_df_simulated[[i]]$new_study_id
                                            %in% no_wl_ids,]

# count studies 
study_count_no_wl_study <- count_studies(df_long_for_metan[df_long_for_metan$new_study_id %in% no_wl_ids,])
# CHARLOTTE please check
# CB come back to this, possible problem.

@@

# D. Estimate Means and CIs without WL and CAU --------------------------------------- 
# grab the ids for no waitlist and cau
no_wl_or_cau_ids <- df_appl_v_orange[df_appl_v_orange$control_type != "wl" & df_appl_v_orange$control_type != "cau",]$new_study_id

# use them to loop over the simulated list to subset all the dataframes.
list_no_wl_or_cau <- list()

  list_no_wl_or_cau[[i]] <- list_df_simulated[[i]][list_df_simulated[[i]]$new_study_id
                                            %in% no_wl_or_cau_ids,]

# count studies 
study_count_no_wl_or_cau_study <- count_studies(df_long_for_metan[df_long_for_metan$new_study_id %in% no_wl_or_cau_ids,])
# CHARLOTTE please check

@@

# count the number of studies
study_count_cdrs_study <- count_studies(df_long_for_metan[df_long_for_metan$new_study_id %in% cdrs_study_ids,])

#CHARLOTTE please check. CB - come back to this, possible problem.

>>>>

# Use those ids to subset all dataframes in the list
# By searching for IDs we have mistakenly included multiple active arms. E.g. for Atkinson which has dulox and fluox. 
# So we need to further subset the simulated dfs. For the active arms, I am filtering out conditions that do not meet our criteria. 
# This leaves all the control conditions from trials where the active is cbt, fluox or esc. 
# We may have multiple controls per study id for this reason, though this isn't a problem 
# conceptually.

@@

# count the number of studies
cbt_fluox_esc_study <- df_long_for_metan %>%
  filter(new_study_id %in% cbt_fluox_esc_study_ids,
         !(arm_effect_size == "cohens_d_active" & !(type %in% c("Fluoxetine", "Escitalopram", "cbt")))) 
study_count_cbt_fluox_esc_study <- count_studies(cbt_fluox_esc_study)
# CB checked, looks good now.

@@

# C. Estimate Means and CIs without WL ---------------------------------------

 # grab the ids for no waitlist
no_wl_ids <-df_appl_v_orange[df_appl_v_orange$control_type != "wl",]$new_study_id

# use them to loop over the simulated list to subset all the dataframes.

list_no_wl <- lapply(list_df_simulated, function(df) {
  df %>%
    filter(new_study_id %in% no_wl_ids) %>%
    filter(!(arm_effect_size == "cohens_d_control" & type == "wl")) 
})

# count studies 
no_wl_studies <- df_long_for_metan %>% 
  filter(new_study_id %in% no_wl_ids) %>%
  filter(!(arm_effect_size == "cohens_d_control" & type == "wl"))
study_count_no_wl_study <- count_studies(no_wl_studies)
# CB checked, looks good!

@@

# D. Estimate Means and CIs without WL and CAU --------------------------------------- 
 # grab the ids for no waitlist and cau
no_wl_cau_ids <- df_appl_v_orange %>%
  filter(!(control_type %in% c("wl", "cau"))) %>%
  pull(new_study_id)

# use them to loop over the simulated list to subset all the dataframes.

list_no_wl_cau <- lapply(list_df_simulated, function(df) {
  df %>%
    filter(new_study_id %in% no_wl_cau_ids) %>%
    filter(!(arm_effect_size == "cohens_d_control" & type %in% c("wl", "cau")))
})

# count studies 
no_wl_cau_studies <- df_long_for_metan %>% 
  filter(new_study_id %in% no_wl_cau_ids) %>%
  filter(!(arm_effect_size == "cohens_d_control" & type %in% c("wl", "cau")))
study_count_no_wl_cau_study <- count_studies(no_wl_cau_studies)
# CB checked, looks good!

@@

# count the number of studies
study_count_cdrs_study <- count_studies(df_long_for_metan[df_long_for_metan$new_study_id %in% cdrs_study_ids,])
# CB checked, correct.
